Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-01-17 paper.tex
Updated intro

The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localization (through IMU measurements and landmark tracking) and image-processing facilities. 
It also provides access to Android's full range of interface tools and I/O options. 
Furthermore, a set of bone-conduction headphones (see \Cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.

\begin{figure}
  \centering
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right).}
  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
\end{figure}

Humans are naturally able to determine the 3D position of a sound source and by exploiting this ability, the real-time guidance instructions can be interpreted without posing a significant cognitive load.
A sound source can be spatialised by adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance).
In our case, only the pan and elevation positions are transmitted to the user to point the camera towards a target object or visual feature.
However, since bone-conduction headphones bypass the outer ear structure, their spectral signature cannot properly be interpreted and we therefore convey the target's elevation angle by adjusting the tone's pitch.
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering~\cite{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}. 
This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
~\cite{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.

@@

Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
%To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localize itself in real-time.
To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\cite{lock2019active} and tested by~\cite{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.

A set of bone-conduction headphones is used as the audio transmission medium.
These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still rely on sound to detect oncoming vehicles and people, for example~\cite{lichtenstein2012headphone}.
Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
The AfterShockz headphones (\Cref{fig:tango-headphone}) were ultimately selected for the aforementioned reasons of non-interference and increased discretion when compared to larger over-ear headphones.

@@

Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.

@@

\begin{figure}
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
~
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis. }
  \Description{The reference system used by the guidance interface showing the camera vector and pan and elevation angles and the pitch gain function used to convey the target's elevation angle. Note the logarithmic scale of the frequency axis. }
\end{figure}

@@

The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound}.
The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
For example, a sound that comes from the individual's right will hit the right ear first with a slightly higher volume compared to the left ear.

@@

A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison}.
To compensate for this, we communicate the target's elevation angle by adjusting the tone's pitch (i.e.\ the sine wave's frequency) as a function of the elevation. 
When the camera vector is at the correct elevation, the tone pitch is set to neutral.
When the target is above or below the camera vector, the pitch is increased or decreased, respectively.
This high/low association scheme is motivated by humans' natural association of high-pitched sounds with elevated sound sources, and low-pitched sounds with source's below the individual's earline~\citep{pratt1930spatial,blauert1997spatial}.
An octave- and semitone-based function is used to adjust the tone's pitch to ensure perceptible changes, while keeping the timbre roughly constant~\citep{shepard1964circularity}.
The pitch is updated at a rate of \SI{10}{\hertz} and changes as the user moves the device.

@@

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
  \Description{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal.}\label{fig:pipeline}
\end{figure}

\subsection{Participant Characterization}\label{sec:participant_characterisation}

A preliminary set of experiments were conducted to characterise the participants' hearing characteristics.
The measured characteristics were each participant's audio localization ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies. 
These results will be used to provide context to the following target search experiment and provide additional insight on any possible biases or limitations.

\subsubsection{Sound Localization}\label{sec:sound_localisation}

@@

The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first one.
The tone difference depends on how well the participant can tell the tones apart.
Like the sound localization experiment, a ``2-up, 1-down'' step process is used: for every two consecutive correct answers, the pitch difference between the tones is halved, while it is doubled for every incorrect answer.
Two-step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
The termination condition is when the two-step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2$) for three consecutive answers.
For example, the experiment will terminate when one sequence is set to \SI{64}{\hertz} and the other is between \SI{32}{\hertz} or \SI{128}{\hertz} for three consecutive guesses.
Pitch differences are measured in semitones, which can be obtained with

@@

To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
The participants were given a Tango device running an app that implements the experimental setup in~\Cref{fig:pipeline}. The app generates a set of virtual targets and presents them to each participant through the audio interface, one at a time. 
The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
Each target's angular position is adjusted and communicated in real-time as the participant points the device around. 
When the participants were confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localization API.\
A total of 28 targets were generated per participant.

@@

Two groups of participants were recruited for the experiments on a volunteer basis. 
Group~\textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 10 people with severe visual impairments (18--55 years old; 36 female, 16 male). 
None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
Each participant performed three sets of experiments each, with the two characterization experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}. 
Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.

@@

\subsection{Characterization of Sound Localization}

\Cref{fig:sound-localisation} shows the results captured from the sound localization experiment where the participants had to select the direction (left or right) that the tone was being played from. 
It can be seen that the vast majority of guesses for both groups were correct.
For Group~\textit{G1}, most of the errors were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behaviour.
This indicates that the participants in \textit{G1} consistently progressed through the distance intervals and we can therefore conclude they had little difficulty determining sound direction.

@@

\subsection{Characterization of Pitch Discrimination}

@@

This work identified a number of uncertainties that can be the focus of future work.
These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behaviour.
Furthermore, casual post-experiment conversations with the participants revealed that some felt that one setting was easier to understand than the others and it can therefore be beneficial to investigate the possibility of adding an auto-adaptation component to the audio signal.
For example, the pitch gradient can be automatically adjusted over time by the device to provide a better match between the human and computer and increase overall target-finding performance.
Indeed, the work by~\cite{gallina2015progressive} may serve as a good guideline for such a system.
Additional feedback modes may also be added to allow for clearer guidance experience for the user, e.g.\ vibration signals to inform them when they point to the target or adjusting the volume to expand the system to three dimensions.
With this kind of audio interface now better understood, it is ready to be implemented into a fully packaged guidance system for people with visual impairments.

>>>>

The prototype platform is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \Cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities. 
It also provides access to Android's full range of interface tools and I/O options. 
Furthermore, a set of bone-conduction headphones (see \Cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.

\begin{figure}
  \centering
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right)~\citep{lock2019bone}.}
  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
\end{figure}

This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load tot he user, given humans' natural ability to determine a sound source 3D positions.
By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
In this case, only the pan and elevation positions are given to the user to instruct them to point the camera towards a target object or visual feature.
However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted, since they are placed on the user's cheekbones and bypass the ears outer structure.
We bypass this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in that dimension.
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}. 
This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
~\citet{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.

@@

Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
%To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localize itself in real-time.
To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\citet{lock2019active} and tested by~\citet{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.

A set of bone-conduction headphones is used as the audio transmission medium~\citep{lock2019bone}.
These headphones sit on a user's cheekbones and conduct the audio signals through the skull into the inner ear, instead of through the outer part like typical over-ear headphones. 
This has the benefit of allowing the user access to ambient sounds and noise, so a person with limited vision can still rely on sound to detect oncoming vehicles and people, for example~\citep{lichtenstein2012headphone}.
Alternative solutions that allow ambient noise through, such as open-back headphones, were also considered, but they still filter the incoming sound and were therefore disregarded.
The AfterShockz headphones (\Cref{fig:tango-headphone}) were ultimately selected for the aforementioned reasons of non-interference and increased discretion when compared to larger over-ear headphones.

@@

Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound,lock2019bone}.
The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.

@@

\begin{figure}
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
~
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis~\citep{lock2019bone}. }
  \Description{The reference system used by the guidance interface showing the camera vector and pan and elevation angles and the pitch gain function used to convey the target's elevation angle. Note the logarithmic scale of the frequency axis. }
\end{figure}

@@

The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound,lock2019bone}.
The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
For example, a sound that comes from the individual's right will hit the right ear first with a slightly higher volume compared to the left ear.

@@

A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison,lock2019bone}.
To compensate for this, we communicate the target's elevation angle by adjusting the tone's pitch (i.e.\ the sine wave's frequency) as a function of the elevation. 
When the camera vector is at the correct elevation, the tone pitch is set to neutral.
When the target is above or below the camera vector, the pitch is increased or decreased, respectively.
This high/low association scheme is motivated by humans' natural association of high-pitched sounds with elevated sound sources, and low-pitched sounds with source's below the individual's earline~\citep{pratt1930spatial,blauert1997spatial}.
An octave- and semitone-based function is used to adjust the tone's pitch to ensure perceptible changes, while keeping the timbre roughly constant~\citep{shepard1964circularity}.
The pitch is updated at a rate of \SI{10}{\hertz} and changes as the user moves the device.

@@

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal~\citep{lock2019bone}. }\label{fig:pipeline}
  \Description{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }
\end{figure}

\subsection{Participant Characterisation}\label{sec:participant_characterisation}

A preliminary set of experiments were conducted to characterise the participants' hearing characteristics.
The measured characteristics were each participant's audio localisation ability on the lateral plane, as well as the participants' ability to discriminate between tones with different frequencies. 
These results will be used to provide context to the following target search experiment and provide additional insight on any possible biases or limitations.

\subsubsection{Sound Localisation}\label{sec:sound_localisation}

@@

The first tone is randomly generated, while the second tone is generated by adding or subtracting some value from the first one.
The tone difference depends on how well the participant can tell the tones apart.
Like the sound localisation experiment, a ``2-up, 1-down'' step process is used: for every two consecutive correct answers, the pitch difference between the tones is halved, while it is doubled for every incorrect answer.
Two-step sequences are again used here, one starting with a large pitch difference ($f_h=2^9=$ \SI{512}{\hertz}) between the tones and the other with a small difference ($f_l=2^1=$ \SI{2}{\hertz}).
The termination condition is when the two-step sequences are within one octave of each other (i.e.\ $\log_2\frac{f_h}{f_l}=2$) for three consecutive answers.
For example, the experiment will terminate when one sequence is set to \SI{64}{\hertz} and the other is between \SI{32}{\hertz} or \SI{128}{\hertz} for three consecutive guesses.
Pitch differences are measured in semitones, which can be obtained with

@@

To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
The participants were given a Tango device running an app that implements the experimental setup in~\Cref{fig:pipeline}. The app generates a set of virtual targets and presents them to each participant through the audio interface, one at a time. 
The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
Each target's angular position is adjusted and communicated in real-time as the participant points the device around. 
When the participants were confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localisation API.\
A total of 28 targets were generated per participant.

@@

Two groups of participants were recruited for the experiments on a volunteer basis. 
Group~\textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 10 people with severe visual impairments (18--55 years old; 36 female, 16 male). 
None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
Each participant performed three sets of experiments each, with the two characterisation experiments in \Cref{sec:participant_characterisation} preceding the final target-search experiment in \Cref{sec:target_search}. 
Both groups were given some time before the target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
Furthermore, to minimise any potential speed/accuracy biases, we asked the participants to focus on finding the targets without worrying about the time it took to complete the task.

@@

\subsection{Characterisation of Sound Localisation}

\Cref{fig:sound-localisation} shows the results captured from the sound localisation experiment where the participants had to select the direction (left or right) that the tone was being played from. 
It can be seen that the vast majority of guesses for both groups were correct.
For Group~\textit{G1}, most of the errors were made at the minimum distance from the centre, i.e.\ the most difficult to guess correctly, which is the expected behaviour.
This indicates that the participants in \textit{G1} consistently progressed through the distance intervals and we can therefore conclude they had little difficulty determining sound direction.

@@

\subsection{Characterisation of Pitch Discrimination}

@@

This work identified a number of uncertainties that can be the focus of future work.
These include questions such as what caused the observed difference in time performance between the groups and whether the constant negative bias observed in \Cref{fig:target-boxplot-error} is indeed caused by a cognitive bias, or whether there is a more complex underlying reason for the behaviour.
Furthermore, casual post-experiment conversations with the participants revealed that some felt that one setting was easier to understand than the others and it can therefore be beneficial to investigate the possibility of adding an auto-adaptation component to the audio signal.
For example, the pitch gradient can be automatically adjusted over time by the device to provide a better match between the human and computer and increase overall target-finding performance.
Indeed, the work by~\citet{gallina2015progressive} may serve as a good guideline for such a system.
Additional feedback modes may also be added to allow for clearer guidance experience for the user, e.g.\ vibration signals to inform them when they point to the target or adjusting the volume to expand the system to three dimensions.
With this kind of audio interface now better understood, it is ready to be implemented into a fully packaged guidance system for people with visual impairments.
